%-------------------------
% Resume in LateX
% Author : Beksultan Abdikaarov
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}



\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemWithURL}[3]{
  \item \small{
      \textbf{#1}{: #2}
    \hfill
      \raggedleft \textit{\href{#3}{\texttt{#3}}}
    \vspace{-4pt}
  }
}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeCertificate}[5]{
  \resumeSubheading
    {#1}{#2}
    {\vspace{-1pt}Issuer: #3}{\href{#4}{\texttt{#5}}}
}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://linkedin.com/in/babdikaarov}{\Large Beksultan Abdikaarov}} \\
  \href{https://github.com/babdikaarov}{github.com/babdikaarov} & Mobile: \href{tel:+97433344627}{+974-333-44627} \\
  \href{https://t.me/babdikaarov}{telegram.me/babdikaarov} & Email: \href{mailto:babdikaarov@gmail.com}{babdikaarov@gmail.com} \\
\end{tabular*}

%-----------EXPERIENCE-----------------


\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Freelance Web Developer}{Remote}
      {Skill Enhancement and Self-Development}{July 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Continuous Learning}
           {Invested in mastering advanced technologies, specializing in both front-end and back-end development tools and frameworks.}
      \resumeItemListEnd

    \resumeSubheading
      {Kashkaldak - kindergarten named after Azim Narmatov }{Doha, Qatar (Remote)}
      {Full Stack Engineer}{March 2024 -- July 2024 (5 months)}
      \resumeItemListStart
        \resumeItem{Project Architect}
          {Engineered a digital transformation for client documentation, enabling streamlined operations and enhanced efficiency.}
        \resumeItem{Google Search Optimization}
          {Implemented SEO strategies, resulting in top search rankings for relevant queries and ensuring the kindergarten appears first in search results.}
        \resumeItem{PWA Enhancement and XSchedule Customization}
          {Upgraded Progressive Web App (PWA) features and customized the XSchedule library to meet specific requirements, resulting in superior performance and functionality.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 -- Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd

%-------------------------------------------

   \resumeSubheading
      {Cool Band - famous band group in Bishkek }{Doha, Qatar (Remote)}
      {Front End Team Lead}{November 2023 -- April 2024 (6 months)}
      \resumeItemListStart
        \resumeItem{Project Leadership}
          {Directed project development, elevating overall efficiency by 200\% and tutoring version control practices that ensured a smooth Git flow.}
        \resumeItem{UI/UX Optimization}
          {Collaborated with designers to enhance UI/UX, significantly improving user experience and engagement, focusing on design and accessibility}
        \resumeItem{Admin UI Development}
          {Decreased development time by 40\% by designing and implementing a streamlined admin panel with responsive design.}
        \resumeItem{Team Productivity}
          {Boosted team output by 25\% through improved collaboration processes and effective communication}
        \resumeItem{API Integration}
          {Orchestrated smooth API integration with the back-end, resolving over 10 integration challenges.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItemWithURL
      {Cool Band}
      {Developed a presentation page and a content management system (CMS) to manage effectively and showcase their business model.}
      {https://cool.kg}
    \resumeSubItemWithURL
      {Kashkaldak Kindergarten}
      {Engineered a comprehensive digital solution to transition document management online. Created presentational layer with advanced content manging system.}
      {https://kashkaldak.edu.kg}
    \resumeSubItemWithURL
      {OpenGraph Service}
      {Created a service for retrieving Open Graph data, enabling rich link previews and enhancing the presentation of shared links.}
      {https://babdikaarov.home.kg}
    % \resumeSubItemWithURL
    %   {HelloItSafari}
    %   {Conceptualized and developed a Hugo-based static site to showcase skills in building efficient static websites with an integrated content management interface.}
    %   {https://helloitsafari.netlify.app}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Codecademy}{Online}
      {Software Engineer}{Mar 2022 -- Apr 2024}
    % \resumeSubheading
    %   {Jusup Balasagyn Kyrgyz National University}{Bishkek, Kyrgyzstan}
    %   {Master's Degree in Law; GPA: 3.73}{2014 -- 2016}
  \resumeSubHeadingListEnd


%-----------Certificates-----------------
\section{Certificates}
  \resumeSubHeadingListStart
    \resumeCertificate
      {Full-Stack Engineer}{Apr 2024}
      {Codecademy}
      {https://www.codecademy.com/profiles/BeksultanAbdikaarov/certificates/ffd0f42cce1a44e9a0108b365047a0a6}
      {Certificate ID: 660B4C0053}
    \resumeSubHeadingListEnd



%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: HTML/CSS, JavaScript, TypeScript, NodeJs, Go, SQL}
   }
   \item{
     \textbf{Technologies}{: Git, React, Redux, React Router, Next.js, PostgreSQL, Sass, Tailwind CSS, Hugo, DecapCMS, Tanstack Form, ReactAdmin, Strapi CMS, PWA, Docker, Nginx, Gin Framework, Colly Package, AWS EC2, Netlify, NPM}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

